### 2013-05-08 inst/examples/BUGS/allen.Rmd
subset plotting of simulations (for slides potentially)
add a movie of data

>>>>

```{r}
dt

```{r Figure3a}
dt$reps <- as.factor(dt$reps) 
setkey(dt, method, reps)

require(animation)
saveMovie({
  for(j in sample(dt$reps, 10)){
    ricker <- dt[J("Ricker", j)]
    for (i in seq(1, max(dt$time), by=5)) {
      print(
        ggplot(subset(ricker, time <= i), 
               aes(time, fishstock, group=interaction(reps,method), color = method), alpha=.9) + 
          geom_line() + xlim(0, max(dt$time)))
    }
  }
}, interval = 0.1, movie.name = "wrong-model.gif", ani.width = 600, ani.height = 600)
